Newly Left-Behind Children's Educational Performance Drops Slightly After Parental Migration

### 2023-06-09 appendix.Rmd
Update code, writing, bibliography

# Tables

```{r tab-reg-cog-adj}
table_adj_cog
```

```{r tab-reg-ttl-adj}
table_adj_ttl
```

```{r tab-reg-m-adj-cog}
table_m_adj_cog
```

```{r tab-reg-m-adj-ttl}
table_m_adj_ttl
```

@@

>>>>

(ref:cog-dif) Changes in cognitive test score

(ref:ttl-dif) Changes in academic exam score

(ref:migr) for newly left-behind students and non-left-behind students

(ref:migr-type) by household migration arrangement

(ref:cobalt-match) Covariate balance before and after matching

(ref:cobalt-any) by any parent migration

(ref:cobalt-fa) by father-only migration

(ref:cobalt-mo) by mother-only migration

(ref:cobalt-both) by both parents migration

```{r v-plot-cog, fig.cap = paste("(ref:cog-dif)", "(ref:migr)"), out.height='40%', warning=FALSE}
fig_cog
```

```{r v-plot-ttl, fig.cap = paste("(ref:ttl-dif)", "(ref:migr)"), out.height='40%', warning=FALSE}
fig_ttl
```

```{r v-plot-cog-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)"), out.height='40%', warning=FALSE}
fig_cog_by_migration_type
```

```{r v-plot-ttl-1, fig.cap = paste("(ref:ttl-dif)", "(ref:migr-type)"), out.height='40%', warning=FALSE}
fig_ttl_by_migration_type
```

@@

```{r cobal-any, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-any)"), out.height='40%'}
m.out |> love.plot(
  threshold = c(m = .1),
  binary = "std", 
  limits = c(0, 0.55),
  abs = T
  )
```

```{r cobal-mo, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-mo)"), out.height='40%'}
m.out_mo_only |> love.plot(
  threshold = c(m = .1),
  binary = "std", 
  limits = c(0, 0.55),
  abs = T
  )
```

```{r cobal-fa, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-fa)"), out.height='40%'}
m.out_fa_only |> love.plot(
  threshold = c(m = .1),
  binary = "std", 
  limits = c(0, 0.55),
  abs = T
  )
```

```{r cobal-both, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-both)"), out.height='40%'}
m.out_both |> love.plot(
  threshold = c(m = .1),
  binary = "std", 
  limits = c(0, 0.55),
  abs = T
  )
```
